\documentclass[11pt, a4paper]{article}
\usepackage{mathptmx}
\usepackage{ragged2e}
\usepackage[a4paper, left=1in, right=1in, top=2in, bottom=2in]{geometry}
\pagenumbering{gobble}
\date{}

\begin{document}

  \begin{flushleft}
    Radinal Shidiq Saragih

    radinals13@gmail.com

    123-456-789

    Cianjur, West Java

    May 19, 2024

    \vspace{0.5cm}

    The Editor

    PT. Kompas Cyber Media

    Palmerah Selatan Street, No. 22 – 28

    Central Jakarta, DKI Jakarta

    \vspace{0.5cm}

    Dear Editor,

    \vspace{0.5cm}

    I am writing to express my concerns and also many others in my
    neighbourhood regarding the newly built chemical factory in the
    middle of my city. I feel that the media need to give more attetion
    on this problem, and especially on how it has negatively affected our lives.

    \vspace{0.2cm}

    Firstly, the area near the factory has become very polluted. I myself is
    living just a few blocks from the factory, and every morning the air can
    be felt to be so polluted, i and many others have reverted to using masks
    for when going outside.

    \vspace{0.2cm}

    Secondy, a portion of the citizens in the area, especially the more
    vulnerable age groups such as the elderly and childrens has been having
    numerous cases of respiratory infections. This is very alarming to
    say the least, and a number of families have chosen to move out of the
    area because of it.

    \vspace{0.2cm}

    Additionally, there have been attemps to contact the factory management
    to send in our complaints, first by the locals in the neighbourhood,
    and then by the city officials itself, but months has passed without any
    response, and there is no signs of them lowering there pollution output.

    \vspace{0.2cm}

    I urge the newspaper in to raise awareness to our situation,
    in hopes that a solution can be found, so I and many others can
    live peacefully and not having to fear the air around us.

    \vspace{0.5cm}

    Thank you for your attention on this issue.

    \vspace{0.2cm}

    Sincerely,

    Radinal Shidiq Saragih
  \end{flushleft}

\end{document}
